---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# actuaryr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/zchmielewska/actuaryr.svg?branch=master)](https://travis-ci.org/zchmielewska/actuaryr)
<!-- badges: end -->

The goal of actuary package is to support the actuarial modelling.

You can install actuaryr package with:
```{r}
install.packages("actuaryr")
library(actuaryr)
```

## Date reference functions

Retrieve the date in reference to the base date.

Build a function using `dref_` + first letters of the reference day.


|                   | of month       | of quarter     | of year        |
|-------------------|----------------|----------------|----------------|
| first day         | `dref_fdom()`  | `dref_fdoq()`  | `dref_fdoy()`  |
| first working day | `dref_fwdom()` | `dref_fwdoq()` | `dref_fwdoy()` |
| last day          | `dref_ldom()`  | `dref_ldoq()`  | `dref_ldoy()`  |
| last working day  | `dref_lwdom()` | `dref_lwdoq()` | `dref_lwdoy()` |

Examples:

```{r}
dref_fdom("2019-09-21")
dref_fwdoq("2019-09-21")
dref_ldoy("2019-09-21")
dref_lwdom("2019-09-21")
```

## Compare

Compare two tables with `compare`.

```{r}
x <- data.frame(
  v1 = 1:3,
  v2 = 4:6
)
y <- data.frame(
  v1 = 1:3,
  v2 = 7:9
)
compare(x, y)
```

