---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# actuary

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/zchmielewska/actuaryr.svg?branch=master)](https://travis-ci.org/zchmielewska/actuaryr)
<!-- badges: end -->

The goal of actuary package is to support the actuarial workload.

## Example

Retrieve the date in reference to the base date.
```{r}
library(actuaryr)
```

Retrieve:

* the first day of a month
* the first day of a quarter
* the first day of an year

```{r}
dref_fdom("2019-09-21")
dref_fdoq("2019-09-21")
dref_fdoy("2019-09-21")
```

Retrieve:

* the first working day of a month
* the first working day of a quarter
* the first working day of an year

```{r}
dref_fwdom("2019-09-21")
dref_fwdoq("2019-09-21")
dref_fwdoy("2019-09-21")
```

Retrieve:

* the last day of a month
* the last day of a quarter
* the last day of an year

```{r}
dref_ldom("2019-09-21")
dref_ldoq("2019-09-21")
dref_ldoy("2019-09-21")
```

Retrieve:

* the last working day of a month
* the last working day of a quarter
* the last working day of an year

```{r}
dref_lwdom("2019-09-21")
dref_lwdoq("2019-09-21")
dref_lwdoy("2019-09-21")
```
